A holomorphic approach to membranes and fivebranes

### 2022-06-16 fivebranes/twisted.tex
lag

As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface, with some number of twisted `fivebranes' wrapping 
\[
0 \times 0 \times C \subset \R \times \C \times C .
\]
It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$. 
Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background. 
We proceed to describe the twisted version of states at the boundary of this version of $AdS$. 
We first proceed before turning on the backreaction.

@@

Modifications of the boundary condition at the point $z = 0$ on the boundary take the form
\[
\alpha = f(w) \delta^{(r)}_{z=0} 
\]
where $f$ is some holomorphic function. 
Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$. 
It is convenient to parameterize such boundary modifications algebraically by expressions of the form 
\[
\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
\]

@@

We first consider the situation of backreacting some number of (twisted) fivebrans.
Let $Z$ be a three-fold that the fivebranes wrap. 
Let $V\to Z$ a rank 2 holomorphic vector bundle such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$. 
The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$. 
The eleven-manifold we place our theory on is $\R\times X_V$, which we can view as the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.

>>>>

As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping 
\[
0 \times 0 \times C \subset \R \times \C \times C .
\]
It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$. 
Denote by $(t,w)$ the fiber coordinates.
Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background. 
We proceed to describe the twisted version of states at the boundary of this version of $AdS$. 
We first proceed before turning on the backreaction.

@@

Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
\[
\alpha = f(w) \delta^{(r)}_{z=0} 
\]
where $f$ is some holomorphic function. 
Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$. 
It is convenient to parameterize such boundary modifications algebraically by expressions of the form 
\[
\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
\]

The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
The phase space at the boundary $C$ can be identified with the following cohomology
\[
\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
\]
where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation. 
We refer to the section below for a reminder on this geometric structure.

The phase space is equipped with a natural symplectic form given by
\[
\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
\]
There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C \setminus 0$ which extends to zero. 
The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.

@@

We now consider the situation of backreacting some number of (twisted) fivebranes in our eleven-dimensional model.
Let $Z$ be a three-fold that the fivebranes wrap. 
We also fix a rank 2 holomorphic vector bundle $V\to Z$ such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$. 
The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$. 
The eleven-manifold we place our theory on is $\R\times X_V$, which we can view as the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
